---
title: "Preliminary Analysis Quiz"
author: "Sean Angiolillo"
date: "3/13/2018"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To continue this week's problem set, please use the West Virginia dataset and the steps outlined in this Unit to:

* Perform a linear regression with a segmented regression specification

* Have R report a summary of the results

```{r message=FALSE}
library(readr)
dat <- read_csv("antipsychotic_study.csv")
dat$time <- 1:nrow(dat)
dat$level <- c(rep(0,8),rep(1,11))
dat$trend <- c(rep(0,8), 1:11)

model_ols <- lm(marketshare ~ time + level + trend, data=dat)
summary(model_ols)
confint(model_ols)
```


## Question 1

With reference to the standard regression for the West Virginia data, what are your estimates of the following variables:

The existing level?

```{r}
coef(model_ols)[1]
```

 The pre-existing trend per quarter?

```{r}
coef(model_ols)[2]
```
 
The estimated level change following the prior authorization policy?

```{r}
coef(model_ols)[3]
```

The estimated change in the trend per quarter following the policy change?

```{r}
coef(model_ols)[4]
```


## Question 2

Based on your standard model results, did the policy in West Viginia lead to a:

* Level increase in market share

* Level increase and trend decrease in market share

* Trend decrease in market share

* **Level decrease and trend decrease in market share**

*Explanation*
The results of the model suggest a statistically significant decrease in both the level and trend of market share following the start of the prior authorization policy.